Scalable Clustering of Genotype Information using MapReduce

### 2015-02-11 doc/publications/journal2014/paper.tex
Updates

\begin{table*}[!t]
\processtable{Resources allocated and time taken.\label{Tab:01}}
{\begin{tabular}{ll|cc|cc|rr|c}\toprule
Tool & Dataset & \multicolumn{2}{ c |}{Preprocesing (GB)} & \multicolumn{2}{ c |}{Clustering (GB)} & \multicolumn{2}{ c |}{Time} & Accuracy\\
& & map & reduce  & map & reduce  & pre-processing & clustering & \\\midrule
        R &\NinteenPhaseone{} & - & - & - & - & 55m 41s & 7s &0.614\\
        Mahout & \NinteenPhaseone{} & 1536 & 3072 & 1536 & 3072 & 6m 10s & 8m 32s & 0.705\\
        & \OnePhaseone{} & 1536 & 3072 & 1536 & 3072 & 9m 52s & 12m 08s & 0.771\\
        & \SevenPhaseone{} & 1536 & 3072 & 4096 & 4096  & 60m 35s & 5h 44m & 0.716\\
        & \FullPhaseone{} & 1536 & 3072 & 6144 & 6144  & 108m 47s &  & \\
        & \OnePhasethree{} & 1536 & 3072 & 1536 & 3072 & 23m 27s & 21m 14s & 0.873\\
        & \ThreePhasethree{} & 1536 & 3072 & 2048 & 4096 & 63m 49s & 93m 18s & 0.871\\\
        & \FullPhasethree{} & 1536 & 3072 & 6144 & 6144 & 5h 36m & 21h 5m &0.623\\\botrule
\end{tabular}}{The resources allocated to each MapReduce yarn-container and time taken for the job(s) to complete.}
\end{table*}

>>>>

\begin{table*}[!t]
\processtable{Resources allocated and time taken.\label{Tab:01}}
{\begin{tabular}{ll|cc|cc|rr|c}\toprule
Tool & Dataset & \multicolumn{2}{ c |}{Preprocesing (GB)} & \multicolumn{2}{ c |}{Clustering (GB)} & \multicolumn{2}{ c |}{Time} & Accuracy\\
& & map & reduce  & map & reduce  & pre-processing & clustering & \\\midrule
        R &\NinteenPhaseone{} & - & - & - & - & 55m 41s & 7s &0.614\\
        Mahout & \NinteenPhaseone{} & 1536 & 3072 & 1536 & 3072 & 6m 10s & 8m 32s & 0.705\\
        & \OnePhaseone{} & 1536 & 3072 & 1536 & 3072 & 9m 52s & 12m 08s & 0.771\\
        & \SevenPhaseone{} & 1536 & 3072 & 4096 & 4096  & 43m 56s & 5h 44m & 0.716\\
        & \FullPhaseone{} & 1536 & 3072 & 6144 & 6144  & 85m 29s & 7h 43m & 0.723\\
        & \OnePhasethree{} & 1536 & 3072 & 1536 & 3072 & 23m 27s & 21m 14s & 0.873\\
        & \ThreePhasethree{} & 1536 & 3072 & 2048 & 4096 & 63m 49s & 93m 18s & 0.871\\\
        & \FullPhasethree{} & 1536 & 3072 & 6144 & 6144 & 5h 36m & 21h 5m &0.623\\\botrule
\end{tabular}}{The resources allocated to each MapReduce yarn-container and time taken for the job(s) to complete.}
\end{table*}
